%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for CV/Resume
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
%
% Adapted to be an Rmarkdown template by Mitchell O'Hara-Wild
% 23 November 2018
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%
%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt,a4paper,]{awesome-cv}

% Configure page margins with geometry
\usepackage{geometry}
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}


% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight

\colorlet{awesome}{awesome-red}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

\def\endfirstpage{\newpage}

%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right

\name{Dr Arran Hamlet}{}

\position{Epidemic Intelligence Service Officer}
\address{Centers for Disease Control and Prevention, Atlanta, USA}

\email{\href{mailto:arranh92@gmail.com}{\nolinkurl{arranh92@gmail.com}}}
\github{arranhamlet}
\linkedin{arranhamlet}

% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \skype{skype-id}
% \reddit{reddit-id}

\quote{Infectious disease epidemiologist and mathematical modeller with
extensive experience in data analysis and statistical/mechanistic
modelling to inform outbreak response and public health policy.}

\usepackage{booktabs}

\providecommand{\tightlist}{%
	\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

%------------------------------------------------------------------------------



% Pandoc CSL macros
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{2em}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\honortitlestyle{#1}}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\honordatestyle{#1}}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
% 2019-02-14 Chris Umphlett - add flexibility to the document name in footer, rather than have it be static Curriculum Vitae
\makecvfooter
  {February, 2024}
    {Dr Arran Hamlet~~~·~~~Curriculum Vitae}
  {\thepage}


%-------------------------------------------------------------------------------
%	CV/RESUME CONTENT
%	Each section is imported separately, open each file in turn to modify content
%------------------------------------------------------------------------------



\hypertarget{education}{%
\section{Education}\label{education}}

\begin{cventries}
    \cventry{Imperial College London}{PhD titled 'Yellow fever in South America: The role of environment and host on transmission dynamics'}{Jan 2017-Jan 2020}{London, United Kingdom}{\begin{cvitems}
\item Looked at understanding the epidemiology of yellow fever across South America, with a focus on Brazil, examining the roles of climate, environment and host. Employed a variety of statistical and mechanistic modelling techniques. Worked with the WHO, the Brazilian Ministry of Health and the university Fundação Oswaldo Cruz.
\item Supervised by Dr Tini Garske and Professor Neil Ferguson, fully funded by the UK Medical Research Council.
\end{cvitems}}
    \cventry{Imperial College London}{MSc in Epidemiology}{Oct 2014-Oct 2015}{London, United Kingdom}{\begin{cvitems}
\item Awarded a distinction for my dissertation project titled 'The Seasonality of Yellow Fever in Africa.'
\end{cvitems}}
    \cventry{Queen Mary University of London}{BSc in Biology with Psychology}{Sep 2011-May 2014}{London, United Kingdom}{\begin{cvitems}
\item Focus on Evolutionary Biology and Neuroscience.
\end{cvitems}}
\end{cventries}

\hypertarget{employment}{%
\section{Employment}\label{employment}}

\begin{cventries}
    \cventry{Centers for Disease Control and Prevention}{Epidemic Intelligence Service Officer (Washington State Department of Health)}{July 2022-}{Seattle, USA}{\begin{cvitems}
\item \textbf{Select projects below.}\\
\item \textbf{Lead on an Epi-Aid investigating the rise in detections of Corynebacterium diphtheriae in Washington state}.
    \\ - Co-lead of a multidisciplinary team from local, state and federal agencies, tasked with investigating the increase in C. diphtheriae detections in Washington State, 2018-2023. 
    \\ - Organized meetings and coordination with local health jurisdictions and hospital system partners to gain access to medical records for chart abstraction, and to understand the context of the increases.
    \\ - Conducted interviews with laboratory directors to understand changes in testing practices, and with partners providing housing and medical care to those experiencing homelessness.
    \\ - Analysis currently ongoing, focusing on changes in transmission and surveillance, the clinical course and social factors related to the increase in detections.
\item \textbf{Lead on estimating the prevalence of long COVID in Washington}.
    \\ - Created a mathematical model using WA DOH data to estimate age, sex, race-ethnicity, and county level prevalence of long COVID over time. 
    \\ - The method was designed and validated with subject matter experts from WA DOH and the CDC to produce a highly flexible approach that integrated existing data sources with the latest findings from scientific literature.
    \\ - Results presented to CSTE, WA DOH leadership, and used in discussions with the Washington State Senate for long COVID advocacy and the positioning of resources.
    \\ - Manuscript under review and the approach is highlighted in a CSTE position paper.
\item \textbf{Lead on an outbreak investigation of gastrointestinal illness on the Pacific Crest Trail}.
    \\ - Lead the outbreak investigation and response. This included, survey design, patient interviews, epidemiological analysis and environmental sampling of pit latrines and shared use facilities.
    \\ - The findings led to changes in WA DOH policy on the use of social media in outbreak investigation, a MMWR article was published and presentations given at EIS and CSTE conferences.
\item \textbf{Evaluation of the rabies surveillance system}.
    \\ - Compared existing rabies mandatory reporting with syndromic surveillance collected from emergency departments and urgent care centers on potential rabies exposures, and with recorded post-exposure prophylaxis. 
    \\ - Identified clear gaps in certain counties reporting of rabies, with some of these reporting less than 1 in 10 estimated rabies exposures.
    \\ - Currently assessing whether we can use these alternative data systems to capture a more accurate understanding of human-rabies encounters, and remove potential rabies exposure as a notifiable condition.
\end{cvitems}}
\end{cventries}

\begin{cventries}
    \cventry{}{}{}{}{\begin{cvitems}
\item \textbf{Tuberculosis in the correctional system.}.
    \\ - Part of the WA DOH team, supervising and responding to Tuberculosis in the WA correctional system following the largest outbreak in decades. Provided leadership and analytical support.
\item \textbf{Malaria in Uganda and Ethiopia}.
    \\ - Working with the CDC malaria group to analyse a study looking at increasing funding to community healthcare workers during 2021-2022.
    \\ - Working with the Presidents Malaria Initiative and PATH to provide subnational estimates of the impact of Anopheles stephensi on malaria transmission in Ethiopia.
\end{cvitems}}
    \cventry{Imperial College London}{Visiting Researcher}{Jun 2022-}{London, United Kingdom}{\begin{cvitems}
\item Visiting researcher for mathematical and statistical modelling of malaria and yellow fever.
\item Provide direction and feedback for projects, reviewing manuscripts and planning strategic research goals.
\end{cvitems}}
    \cventry{Imperial College London}{Postdoctoral Researcher (Malaria)}{Jan 2020-Jun 2022}{London, United Kingdom}{\begin{cvitems}
\item Involved in a variety of projects assessing the public health impact of various control measures on the burden of malaria across Africa using mechanistic transmission models.
\\ - Several of these outputs were used by organizations such as the WHO, IVCC, MedAccess and Ministries of Health to understand the potential benefits of different malaria control strategies and the utility of next generation bednets such as Piperonyl butoxide (PBO) or Interceptor® G2 in areas of high insecticide resistance.
\item Assessed the impact of disruption caused by the SARS-CoV-2 pandemic on malaria control across Africa. Results published Nature Medicine as joint first author.
\item Lead researcher on a piece of work assessing the potential impact of Anopheles stephensi establishment on malaria transmission in Ethiopia.
\\ - This piece of work was conducted with Abt Associates and the Presidents Malaria Initiative.
\\ - The findings were published in BMC Medicine, and have been widely cited by the WHO and PMI in their advocacy work.
\end{cvitems}}
    \cventry{Imperial College London}{Postdoctoral Researcher (Nigeria COVID-19 response)}{Apr 2020-Dec 2020}{London, United Kingdom}{\begin{cvitems}
\item Lead researcher for Imperial College London's data analytics and modelling support for the Nigerian Government.
\item Conducted rapid analysis to answer specific questions in order to provide evidence for policy decisions to be made by the Nigerian Presidential Task Force.
\item Produced a multitidue of reports as well as regular state-specicic analysis that fed into NCDC, US CDC and UK Department for International Development decision making.
\item A number of position papers can be found at https://statehouse.gov.ng/covid19/2020/09/18/evidence-based-guidance-on-measures-to-curb-the-spread-of-covid-19/.
\end{cvitems}}
    \cventry{Imperial College London}{Postdoctoral Researcher (COVID-19 response)}{Feb 2020-Dec 2020}{London, United Kingdom}{\begin{cvitems}
\item Provided technical support and input for numerous reports and projects, with a focus on work in Low-to-Middle-Income Countries (LMIC) and on quantifying the underascertainment of mortality. Work contributed to several peer reviewed papers and numerous position papers.
\item Seconded through the Global Outbreak Alert and Response Network to provide analytical support for the WHO in Geneva Feb - Apr 2020 to understand the initial spread of COVID-19.
\end{cvitems}}
    \cventry{Imperial College London}{PhD in Infectious Disease Modelling}{Jan 2017 - Jan 2020}{London, United Kingdom}{\begin{cvitems}
\item PhD thesis titled 'Yellow fever in South America: The role of environment and host on transmission dynamics'.
\item Explored the role of climate, landcover and zoonotic reservoirs on the distribution of yellow fever in South America. Additional work focussed on estimating the vaccination coverage of yellow fever globally over time.
\end{cvitems}}
    \cventry{Imperial College London}{Research Assistant}{Oct 2015 - Dec 2016}{London, United Kingdom}{\begin{cvitems}
\item Outbreak analysis and response for the 2015-2016 outbreak in Angola and the Democratic Republic of the Congo working with the World Health Organization (WHO).\\ - This involved rapid modelling and data analytics to answer questions on the spread and suitability of the environment for transmission, and planning vaccination campaign strategies to stop the outbreak.\\ - Hired as a consultant to produce a report on strategies for optimally reducing the risk of yellow fever transmission in Africa, and the potential for global spread.
\item Responsible for estimating population-level vaccination coverage across Africa and the development of an open-source tool to explore this information. Currently utilised by researchers and the WHO.
\end{cvitems}}
\end{cventries}
\newpage

\hypertarget{consultancy}{%
\section{Consultancy}\label{consultancy}}

\begin{cventries}
    \cventry{AppliedEpi}{Course Instructor and Curriculum Designer}{Jan 2022 - }{Online}{\begin{cvitems}
\item AppliedEpi is the non-profit behind the Epidemiologist R Handbook, used by almost 2 million epidemiologists worldwide. Since early 2022 they have offered courses teaching applied R coding to epidemiologists, running over a hundred courses for dozens of Ministries of Health globally as well as the WHO, CDC and various other institutions.
\item I was responsible for designing and creating several of the modules on data management and analysis, as well as the sole designer and creator of the Advanced Statistics in R course.
\item I have lead or demonstrated on courses for almost a dozen agencies, including the Health Departments for Michigan, Wales, Canada, Camobdia, Kazakhstan.
\item Currently lead author responsible for a team of epidemiologists writing chapters of data analysis and regression in a field manual for applied epidemiologists.
\end{cvitems}}
    \cventry{World Health Organization}{Epidemiologist: COVID-19}{Feb 2020 - Apr 2020}{Geneva, Switzerland}{\begin{cvitems}
\item Provided technical support for the WHO in the Health Emergency Information and Risk Assessment (HIM) pillar through GOARN deployment
\item Work involved exploring and quantifying mortality, transmission and country specific impacts through data analysis and visualisation in real time as the COVID-19 pandemic unfolded. Aspects of data visualisation acknowledged in https://worldhealthorg.shinyapps.io/covid/.
\item Continued to provide adhoc support till Dec 2020.
\end{cvitems}}
    \cventry{World Health Organization}{Epidemiologist: Yellow fever}{Jul 2016 - Sep 2016}{Geneva, Switzerland}{\begin{cvitems}
\item Commissioned to produce a report evaluating the risk of outbreaks of yellow fever across Africa as a result of ongoing transmission in Angola and the Democratic Republic of the Congo and the potential for introduction into Asia.
\end{cvitems}}
    \cventry{Ozygen Systems}{Epidemiologist}{Feb 2016 - Mar 2016}{London, United Kingdom}{\begin{cvitems}
\item Hired to produce a report on numerous pathogens involved in nosocomial infection and to evaluate the applicability of ozone decontamination technology in UK healthcare settings to limit their spread.
\end{cvitems}}
\end{cventries}

\hypertarget{funding-awards}{%
\section{Funding awards}\label{funding-awards}}

\begin{cventries}
    \cventry{Imperial College London}{MRC Pump Priming (£23,000)}{Nov 2019}{London, United Kingdom}{\begin{cvitems}
\item Jointly awarded £23,000 with co-PI Natsuko Imai to run a week long training workshop in Rio de Janeiro focusing on the use of mathematical models in outbreak response and policy.
\item Course was run collaboratively with the Brazilian Ministry of Health and Fundação Oswaldo Cruz (Fiocruz).
\end{cvitems}}
    \cventry{Imperial College London}{MRC Exceptional Training Opportunity}{Oct 2017/Aug 2018/Jun 2019}{London, United Kingdom}{\begin{cvitems}
\item Oct 2017: Awarded £650 to travel to the WHO in Geneva, Switzerland to present my work on yellow fever and discuss with the yellow fever team how my PhD can provide support for their activities.
\item Aug 2018: Awarded £2220 to travel to Rio de Janiro and Brasilia, Brazil, and present my results on modelling yellow fever in South America at a meeting co-hosted by the Brazilian Ministry of Health and the Pan American Health Organization, as well as to set up a research collaboration with Fiocruz.
\item Jun 2019: Awarded £1719 to travel to Bogota, Colombia to lecture and demonstrate on a course coordinated between Imperial College London, Instituto Nacional De Salud and Pontificia Universidad Javeriana Bogota which aimed to give an introduction to infectious disease modelling.
\end{cvitems}}
\end{cventries}

\hypertarget{teaching}{%
\section{Teaching}\label{teaching}}

\begin{cventries}
    \cventry{Imperial College London}{Shortcourse co-organiser}{Jan 2021 - Sep 2021}{London, United Kingdom}{\begin{cvitems}
\item Co-organiser on the departments 'Mathematical modelling for the control of infectious diseases' short course, run since 1990 and designed to teach pubic health professionals about infectious disease modelling.
\item Responsible for helping redesign, and restructure, the course in order to deliver it fully online in light of the ongoing COVID-19 pandemic.
\end{cvitems}}
    \cventry{University of São Paulo}{PhD Assessor}{Oct 2020-Jun 2023}{São Paulo, Brazil}{\begin{cvitems}
\item Examining progress and assisting with the research of a PhD student's project titled 'Spatio-temporal dynamics of yellow fever in Brazil'.
\end{cvitems}}
    \cventry{Imperial College London}{MSc Dissertation Supervisor}{May 2020 - Oct 2020}{London, United Kingdom}{\begin{cvitems}
\item Designed and supervised MSc Epidemiology projects looking at the effect of forest fragmentation on yellow fever in Southern Brazil, and exploring the differences in transmission dynamics between yellow fever, dengue and zika.
\end{cvitems}}
    \cventry{Imperial College London}{Graduate Teaching Assistant}{Jan 2017 - Jun 2022}{London, United Kingdom}{\begin{cvitems}
\item Teaching assistant and demonstrator for numerous modules on infectious disease modelling, statistical analysis and epidemiology.
\end{cvitems}}
    \cventry{Imperial College London}{Shortcourse Demonstrator}{Jun 2019}{Bogota, Colombia}{\begin{cvitems}
\item Demonstrator and lecturer on a course coordinated between Imperial College London, Instituto Nacional De Salud and Pontificia Universidad Javeriana Bogota which aimed to give an introduction to infectious disease modelling.
\end{cvitems}}
    \cventry{Imperial College London}{Design and implementation of an online platform for teaching infectious disease modelling}{Jan 2019 - Sept 2019}{London, United Kingdom}{\begin{cvitems}
\item Responsible for liasing between programming team and course organisers to design and translate existing practicals from Berkely Madonna to an online web interface running the Odin language.
\item Highly successful implementation with the platform now being used for both future shortcourses and the MSc Epidemiology at Imperial College London.
\end{cvitems}}
\end{cventries}

\hypertarget{presentations}{%
\section{Presentations}\label{presentations}}

\begin{cventries}
    \cventry{Western States Modeling Symposium}{Estimating the Burden and Distribution of Long COVID in Washington State}{Sep 2023}{Virtual}{}\vspace{-4.0mm}
    \cventry{EIS Conference 2023 and CSTE 2023}{Gastrointestinal illness among hikers on the Washington State Pacific Crest Trail, August–October 2022.}{Apr 2023}{USA}{}\vspace{-4.0mm}
    \cventry{London Malaria Network}{The potential public health consequences of COVID-19 on malaria in Africa}{Oct 2020}{London, United Kingdom}{}\vspace{-4.0mm}
    \cventry{American Society of Tropical Medicine and Hygiene}{Seasonality of agricultural exposure more important than seasonality of climate for predicting yellow fever transmission in Brazil}{Nov 2019}{National Harbor, USA}{}\vspace{-4.0mm}
    \cventry{Outbreak Analysis and Modelling for Public Health}{Statistical and mathematical modelling of yellow fever in South America}{Jun 2019}{Bogota, Colombia}{}\vspace{-4.0mm}
    \cventry{International Conference on One Medicine One Science}{Land-use,  vegetation  and  habitat fragmentation  as  drivers  of  yellow  fever  transmission  in  South America}{Feb 2019}{Chiang Mai, Thailand}{}\vspace{-4.0mm}
    \cventry{Yellow fever forecasting: Embedding   modelling in lessons learnt exercises}{Yellow fever in Brazil - Modelling as a tool to inform outbreak response and public health policy}{Nov 2018}{Brasilia, Brazil}{}\vspace{-4.0mm}
\end{cventries}

\hypertarget{publications}{%
\section{Publications}\label{publications}}

\hypertarget{first-author-publications---7}{%
\subsection{First author publications -
7}\label{first-author-publications---7}}

\begin{cventries}
    \cventry{\textcolor{red}{\textbf{A Hamlet}} , K Begley, S Miko, L Stewart, W Tellier, JG-D Leon, H Booth, S Lippman, A Kahler, A Roundtree, A Hatada, S Lindquist, B Melius, M Goldoft, M Mattioli, M Holshue}{Notes from the Field: Gastrointestinal Illness Among Hikers on the Pacific Crest Trail—Washington, August–October 2022}{Mmwr. Morbidity And Mortality Weekly Report}{2023}{}\vspace{-4.0mm}
    \cventry{\textcolor{red}{\textbf{A Hamlet}} , D Dengela, JE Tongren, FG Tadesse, T Bousema, M Sinka, A Seyoum, SR Irish, JS Armistead, T Churcher}{The potential impact of Anopheles stephensi establishment on the transmission of Plasmodium falciparum in Ethiopia and prospective control measures}{BMC Medicine}{2022}{}\vspace{-4.0mm}
    \cventry{\textcolor{red}{\textbf{A Hamlet}} , DG Ramos, KAM Gaythorpe, APM Romano, T Garske, NM Ferguson}{Seasonality of agricultural exposure as an important predictor of seasonal yellow fever spillover in Brazil}{Nature Communications}{2021}{}\vspace{-4.0mm}
    \cventry{\textcolor{red}{\textbf{A Hamlet}} , KAM Gaythorpe, T Garske, NM Ferguson}{Seasonal and inter-annual drivers of yellow fever transmission in South America}{PLoS Neglected Tropical Diseases}{2021}{}\vspace{-4.0mm}
    \cventry{\textcolor{red}{\textbf{A Hamlet}} }{Yellow fever in South America: The role of environment and host on transmission dynamics}{Imperial College London}{2020}{}\vspace{-4.0mm}
    \cventry{\textcolor{red}{\textbf{A Hamlet}} , K Jean, S Yactayo, J Benzler, L Cibrelus, N Ferguson, T Garske}{POLICI: A web application for visualising and extracting yellow fever vaccination coverage in Africa}{Vaccine}{2019}{}\vspace{-4.0mm}
    \cventry{\textcolor{red}{\textbf{A Hamlet}} , Kév Jean, W Perea, S Yactayo, J Biey, MV Kerkhove, N Ferguson, T Garske}{The seasonal influence of climate and environment on yellow fever transmission across Africa}{PLoS Neglected Tropical Diseases}{2018}{}\vspace{-4.0mm}
\end{cventries}

\hypertarget{additional-publications---32}{%
\subsection{Additional publications -
32}\label{additional-publications---32}}

\begin{cventries}
    \cventry{C Whittaker, \textcolor{red}{\textbf{A Hamlet}} , E Sherrard-Smith, P Winskill, G Cuomo-Dannenburg, PGT Walker, M Sinka, S Pironon, A Kumar, A Ghani, S Bhatt, TS Churcher}{Seasonal dynamics of Anopheles stephensi and its implications for mosquito detection and emergent malaria control in the Horn of Africa}{Proceedings Of The National Academy Of Sciences}{2023}{}\vspace{-4.0mm}
    \cventry{BA Lipton, HN Oltean, RB Capron, \textcolor{red}{\textbf{A Hamlet}} , SP Montgomery, RJ Chancey, VJL Konold, KE Steffl}{Baylisascaris procyonis Roundworm Infection in Child with Autism Spectrum Disorder, Washington, USA, 2022}{Emerging Infectious Diseases}{2023}{}\vspace{-4.0mm}
    \cventry{E-Y Caicedo, K Charniga, A Rueda, I Dorigatti, Y Mendez, \textcolor{red}{\textbf{A Hamlet}} , J-P Carrera, ZM Cucunubá}{Correction: The epidemiology of Mayaro virus in the Americas: A systematic review and key parameter estimates for outbreak modelling}{PLoS Neglected Tropical Diseases}{2023}{}\vspace{-4.0mm}
    \cventry{D Cantoni, M Mayora-Neto, M Derveni, KD Costa, VO Ameh, CT Sabeta, E Wright, SD Scott, ES Giotis, AC Banyard, N Temperton}{Serological evidence of virus infection in Eidolon helvum fruit bats: implications for bushmeat consumption in Nigeria}{Frontiers In Public Health}{2023}{}\vspace{-4.0mm}
    \cventry{G Cuomo-Dannenburg, K McCain, R McCabe, HJT Unwin, P Doohan, RK Nash, JT Hicks, K Charniga, C Geismar, B Lambert, D Nikitin, J Skarp, J Wardle, M Kont, S Bhatia, N Imai, Sv Elsland, A Cori, C Morgenstern, A Morris, A Dighe, \textcolor{red}{\textbf{A Hamlet}} , C Whittaker, D Jorgensen, E Knock, E Unwin, H Thompson, I Routledge, J Hicks, K Fraser, L Geidelberg, L Cattarino, M Baguelin, N Moghaddas, R Nash, S Radhakrishnan, ZC Perez}{Marburg Virus Disease outbreaks, mathematical models, and disease parameters: a Systematic Review}{The Lancet Infectious Diseases}{2023}{}\vspace{-4.0mm}
    \cventry{R McCabe, C Whittaker, RJ Sheppard, N Abdelmagid, A Ahmed, IZ Alabdeen, NF Brazeau, AAA Elhameed, AS Bin-Ghouth, \textcolor{red}{\textbf{A Hamlet}} , R AbuKoura, G Barnsley, JA Hay, M Alhaffar, EK Besson, SM Saje, BG Sisay, SH Gebreyesus, AP Sikamo, A Worku, YS Ahmed, DH Mariam, MM Sisay, F Checchi, M Dahab, BS Endris, AC Ghani, PGT Walker, CA Donnelly, OJ Watson}{Alternative epidemic indicators for COVID-19 in three settings with incomplete death registration systems}{Science Advances}{2023}{}\vspace{-4.0mm}
    \cventry{E Sherrard-Smith, P Winskill, \textcolor{red}{\textbf{A Hamlet}} , C Ngufor, R N'Guessan, MW Guelbeogo, A Sanou, RK Nash, A Hill, EL Russell, M Woodbridge, PK Tungu, MD Kont, T Mclean, C Fornadel, JH Richardson, MJ Donnelly, SG Staedke, S Gonahasa, N Protopopoff, M Rowland, TS Churcher}{Optimising the deployment of vector control tools against malaria: a data-informed modelling study}{The Lancet Planetary Health}{2022}{}\vspace{-4.0mm}
    \cventry{SL Li, AéL Acosta, SC Hill, OJ Brady, MABd Almeida, JdC Cardoso, \textcolor{red}{\textbf{A Hamlet}} , LF Mucci, JTd Deus, FCM Iani, NS Alexander, GRW Wint, OG Pybus, MUG Kraemer, NR Faria, JP Messina}{Mapping environmental suitability of Haemagogus and Sabethes spp. mosquitoes to understand sylvatic transmission risk of yellow fever virus in Brazil}{PLoS Neglected Tropical Diseases}{2022}{}\vspace{-4.0mm}
    \cventry{HA Shah, LR Carrasco, \textcolor{red}{\textbf{A Hamlet}} , KA Murray}{Exploring agricultural land-use and childhood malaria associations in sub-Saharan Africa}{Scientific Reports}{2022}{}\vspace{-4.0mm}
    \cventry{JA Polonsky, S Bhatia, K Fraser, \textcolor{red}{\textbf{A Hamlet}} , J Skarp, IJ Stopard, Sép Hugonnet, L Kaiser, C Lengeler, K Blanchet, P Spiegel}{Feasibility, acceptability, and effectiveness of non-pharmaceutical interventions against infectious diseases among crisis-affected populations: a scoping review}{Infectious Diseases Of Poverty}{2022}{}\vspace{-4.0mm}
    \cventry{C Whittaker, OJ Watson, C Alvarez-Moreno, N Angkasekwinai, A Boonyasiri, LC Triana, D Chanda, L Charoenpong, M Chayakulkeeree, GS Cooke, J Croda, ZM Cucunubá, BA Djaafara, CF Estofolete, ME Grillet, NR Faria, SF Costa, DA Forero-Peña, DM Gibb, AC Gordon, RL Hamers, \textcolor{red}{\textbf{A Hamlet}} , V Irawany, A Jitmuang, N Keurueangkul, TN Kimani, M Lampo, AS Levin, G Lopardo, R Mustafa, S Nayagam, T Ngamprasertchai, N’a’aIH Njeri, ML Nogueira, E Ortiz-Prado, MWP Jr, AN Phillips, P Promsin, A Qavi, AJ Rodger, EC Sabino, S Sangkaew, D Sari, R Sirijatuphat, AC Sposito, P Srisangthong, HA Thompson, Z Udwadia, S Valderrama-Beltran, P Winskill, AC Ghani, PGT Walker, TB Hallett}{Understanding the potential impact of different drug properties on severe acute respiratory syndrome coronavirus 2 (SARS-CoV-2) transmission and disease burden: A modelling …}{Clinical Infectious Diseases}{2022}{}\vspace{-4.0mm}
    \cventry{SL Li, AL Acosta, SC Hill, OJ Brady, MABd Almeida, JdC Cardoso, \textcolor{red}{\textbf{A Hamlet}} , LF Mucci, JTd Deus, F Iani, NS Alexander, GR Wint, OG Pybus, MUG Kraemer, NR Faria, JP Messina}{apping environmental suitability of Haemagogus and Sabethes spp. mosquitoes to understand sylvatic transmission risk of yellow fever virus in Brazi}{PLoS Neglected Tropical Diseases}{2022}{}\vspace{-4.0mm}
    \cventry{P Nouvellet, S Bhatia, A Cori, KEC Ainslie, M Baguelin, S Bhatt, A Boonyasiri, NF Brazeau, L Cattarino, LV Cooper, H Coupland, ZM Cucunuba, G Cuomo-Dannenburg, A Dighe, BA Djaafara, I Dorigatti, OD Eales, SLv Elsland, FF Nascimento, RG FitzJohn, KAM Gaythorpe, L Geidelberg, WD Green, \textcolor{red}{\textbf{A Hamlet}} , K Hauck, W Hinsley, N Imai, B Jeffrey, E Knock, DJ Laydon, JA Lees, T Mangal, TA Mellan, G Nedjati-Gilani, KV Parag, M Pons-Salort, M Ragonnet-Cronin, S Riley, HJT Unwin, R Verity, MAC Vollmer, E Volz, PGT Walker, CE Walters, H Wang, OJ Watson, C Whittaker, LK Whittles, X Xi, NM Ferguson, CA Donnelly}{Reduction in mobility and COVID-19 transmission}{Nature Communications}{2021}{}\vspace{-4.0mm}
    \cventry{C Whittaker, PGT Walker, M Alhaffar, \textcolor{red}{\textbf{A Hamlet}} , BA Djaafara, A Ghani, N Ferguson, M Dahab, F Checchi, OJ Watson}{Under-reporting of deaths limits our understanding of true burden of covid-19}{BMJ}{2021}{}\vspace{-4.0mm}
    \cventry{KAM Gaythorpe, \textcolor{red}{\textbf{A Hamlet}} , K Jean, DG Ramos, L Cibrelus, T Garske, N Ferguson}{The global burden of yellow fever}{Elife}{2021}{}\vspace{-4.0mm}
    \cventry{AB Hogan, P Winskill, OJ Watson, PGT Walker, C Whittaker, M Baguelin, NF Brazeau, GD Charles, KAM Gaythorpe, \textcolor{red}{\textbf{A Hamlet}} , E Knock, DJ Laydon, JA Lees, A Løchen, R Verity, LK Whittles, F Muhib, K Hauck, NM Ferguson, AC Ghani}{Within-country age-based prioritisation, global allocation, and public health impact of a vaccine against SARS-CoV-2: A mathematical modelling analysis}{Vaccine}{2021}{}\vspace{-4.0mm}
    \cventry{OJ Watson, M Alhaffar, Z Mehchy, C Whittaker, Z Akil, NF Brazeau, G Cuomo-Dannenburg, \textcolor{red}{\textbf{A Hamlet}} , HA Thompson, M Baguelin, RG FitzJohn, E Knock, JA Lees, LK Whittles, T Mellan, P Winskill, ICCOVID-19RTBSDBA.DCA.FSGKAMINJELDJ.MSUH.JT.VR 1, N Howard, H Clapham, F Checchi, N Ferguson, A Ghani, E Beals, P Walker}{Leveraging community mortality indicators to infer COVID-19 mortality and transmission dynamics in Damascus, Syria}{Nature Communications}{2021}{}\vspace{-4.0mm}
    \cventry{E-Y Caicedo, K Charniga, A Rueda, I Dorigatti, Y Mendez, \textcolor{red}{\textbf{A Hamlet}} , J-P Carrera, ZM Cucunubá}{The epidemiology of Mayaro virus in the Americas: A systematic review and key parameter estimates for outbreak modelling}{PLoS Neglected Tropical Diseases}{2021}{}\vspace{-4.0mm}
    \cventry{H Fu, H Wang, X Xi, A Boonyasiri, Y Wang, W Hinsley, KJ Fraser, R McCabe, DO Mesa, J Skarp, A Ledda, T Dewé, A Dighe, P Winskill, SLv Elsland, KEC Ainslie, M Baguelin, S Bhatt, O Boyd, NF Brazeau, L Cattarino, G Charles, H Coupland, ZM Cucunuba, G Cuomo-Dannenburg, CA Donnelly, I Dorigatti, OD Eales, RG FitzJohn, S Flaxman, KAM Gaythorpe, AC Ghani, WD Green, \textcolor{red}{\textbf{A Hamlet}} , K Hauck, DJ Haw, B Jeffrey, DJ Laydon, JA Lees, T Mellan, S Mishra, G Nedjati-Gilani, P Nouvellet, L Okell, KV Parag, M Ragonnet-Cronin, S Riley, N Schmit, HA Thompson, HJT Unwin, R Verity, MAC Vollmer, E Volz, PGT Walker, CE Walters, OJ Watson, C Whittaker, LK Whittles, N Imai, S Bhatia, NM Ferguson}{Database of epidemic trends and control measures during the first wave of COVID-19 in mainland China}{International Journal Of Infectious Diseases}{2021}{}\vspace{-4.0mm}
    \cventry{N Raslan, \textcolor{red}{\textbf{A Hamlet}} , V Kumari}{Mental health and psychosocial support in conflict: children’s protection concerns and intervention outcomes in Syria}{Conflict And Health}{2021}{}\vspace{-4.0mm}
    \cventry{Kév Jean, H Raad, KAM Gaythorpe, \textcolor{red}{\textbf{A Hamlet}} , JE Mueller, D Hogan, T Mengistu, HJ Whitaker, T Garske, MN Hocine}{Assessing the impact of preventive mass vaccination campaigns on yellow fever outbreaks in Africa: A population-level self-controlled case series study}{PLoS Medicine}{2021}{}\vspace{-4.0mm}
    \cventry{CA Donnelly, S Bhatia, N Imai, G Cuomo-Dannenburg, M Baguelin, A Boonyasiri, A Cori, Z Cucunubá, I Dorigatti, R FitzJohn, H Fu, K Gaythorpe, A Ghani, \textcolor{red}{\textbf{A Hamlet}} , W Hinsley, D Laydon, G Nedjati-Gilani, L Okell, S Riley, H Thompson, Sv Elsland, E Volz, H Wang, Y Wang, C Whittaker, X Xi, NM Ferguson}{Estimating the number of undetected COVID-19 cases among travellers from mainland China}{Wellcome Open Research}{2021}{}\vspace{-4.0mm}
    \cventry{R Verity, LC Okell, I Dorigatti, P Winskill, C Whittaker, N Imai, G Cuomo-Dannenburg, H Thompson, PGT Walker, H Fu, A Dighe, JT Griffin, M Baguelin, S Bhatia, A Boonyasiri, A Cori, Z Cucunubá, R FitzJohn, K Gaythorpe, W Green, \textcolor{red}{\textbf{A Hamlet}} , W Hinsley, D Laydon, G Nedjati-Gilani, S Riley, SV Elsland, E Volz, H Wang, Y Wang, X Xi, CA Donnelly, AC Ghani, NM Ferguson}{Estimates of the severity of coronavirus disease 2019: a model-based analysis}{The Lancet Infectious Diseases}{2020}{}\vspace{-4.0mm}
    \cventry{S Flaxman, S Mishra, A Gandy, HJT Unwin, TA Mellan, H Coupland, C Whittaker, H Zhu, T Berah, JW Eaton, Mél Monod, AC Ghani, CA Donnelly, S Riley, MAC Vollmer, NM Ferguson, LC Okell, S Bhatt}{Estimating the effects of non-pharmaceutical interventions on COVID-19 in Europe}{Nature}{2020}{}\vspace{-4.0mm}
    \cventry{PGT Walker, C Whittaker, OJ Watson, M Baguelin, P Winskill, \textcolor{red}{\textbf{A Hamlet}} , BA Djafaara, Z Cucunubá, DO Mesa, W Green, H Thompson, S Nayagam, KEC Ainslie, S Bhatia, S Bhatt, A Boonyasiri, O Boyd, NF Brazeau, L Cattarino, G Cuomo-Dannenburg, A Dighe, CA Donnelly, I Dorigatti, SLV Elsland, R FitzJohn, H Fu, KAM Gaythorpe, L Geidelberg, N Grassly, D Haw, S Hayes, W Hinsley, N Imai, D Jorgensen, E Knock, D Laydon, S Mishra, G Nedjati-Gilani, LC Okell, HJ Unwin, R Verity, M Vollmer, CE Walters, H Wang, Y Wang, X Xi, DG Lalloo, NM Ferguson, AC Ghani}{The impact of COVID-19 and strategies for mitigation and suppression in low-and middle-income countries}{Science}{2020}{}\vspace{-4.0mm}
    \cventry{AB Hogan, BL Jewell, E Sherrard-Smith, JF Vesga, OJ Watson, C Whittaker, \textcolor{red}{\textbf{A Hamlet}} , JA Smith, P Winskill, R Verity, M Baguelin, JA Lees, LK Whittles, KEC Ainslie, S Bhatt, A Boonyasiri, NF Brazeau, L Cattarino, LV Cooper, H Coupland, G Cuomo-Dannenburg, A Dighe, BA Djaafara, CA Donnelly, JW Eaton, SLv Elsland, RG FitzJohn, H Fu, KAM Gaythorpe, W Green, DJ Haw, S Hayes, W Hinsley, N Imai, DJ Laydon, TD Mangal, TA Mellan, S Mishra, G Nedjati-Gilani, KV Parag, HA Thompson, HJT Unwin, MAC Vollmer, CE Walters, H Wang, Y Wang, X Xi, NM Ferguson, LC Okell, TS Churcher, N Arinaminpathy, AC Ghani, PGT Walker, TB Hallett}{Potential impact of the COVID-19 pandemic on HIV, tuberculosis, and malaria in low-income and middle-income countries: a modelling study}{The Lancet Global Health}{2020}{}\vspace{-4.0mm}
    \cventry{NC Grassly, M Pons-Salort, EPK Parker, PJ White, NM Ferguson, K Ainslie, M Baguelin, S Bhatt, A Boonyasiri, N Brazeau, L Cattarino, H Coupland, Z Cucunuba, G Cuomo-Dannenburg, A Dighe, C Donnelly, SLv Elsland, R FitzJohn, S Flaxman, K Fraser, K Gaythorpe, W Green, \textcolor{red}{\textbf{A Hamlet}} , W Hinsley, N Imai, E Knock, D Laydon, T Mellan, S Mishra, G Nedjati-Gilani, P Nouvellet, L Okell, M Ragonnet-Cronin, HA Thompson, HJT Unwin, M Vollmer, E Volz, C Walters, Y Wang, OJ Watson, C Whittaker, L Whittles, X Xi}{Comparison of molecular testing strategies for COVID-19 control: a mathematical modelling study}{The Lancet Infectious Diseases}{2020}{}\vspace{-4.0mm}
    \cventry{E Sherrard-Smith, AB Hogan, \textcolor{red}{\textbf{A Hamlet}} , OJ Watson, C Whittaker, P Winskill, F Ali, AB Mohammad, P Uhomoibhi, I Maikore, N Ogbulafor, J Nikau, MD Kont, JD Challenger, R Verity, B Lambert, M Cairns, B Rao, M Baguelin, LK Whittles, JA Lees, S Bhatia, ES Knock, L Okell, HC Slater, AC Ghani, PGT Walker, OO Okoko, TS Churcher}{The potential public health consequences of COVID-19 on malaria in Africa}{Nature Medicine}{2020}{}\vspace{-4.0mm}
    \cventry{KEC Ainslie, CE Walters, H Fu, S Bhatia, H Wang, X Xi, M Baguelin, S Bhatt, A Boonyasiri, O Boyd, L Cattarino, C Ciavarella, Z Cucunuba, G Cuomo-Dannenburg, A Dighe, I Dorigatti, SLv Elsland, R FitzJohn, K Gaythorpe, AC Ghani, W Green, \textcolor{red}{\textbf{A Hamlet}} , W Hinsley, N Imai, D Jorgensen, E Knock, D Laydon, G Nedjati-Gilani, LC Okell, I Siveroni, HA Thompson, HJT Unwin, R Verity, M Vollmer, PGT Walker, Y Wang, OJ Watson, C Whittaker, P Winskill, CA Donnelly, NM Ferguson, S Riley}{Evidence of initial success for China exiting COVID-19 social distancing policy after achieving containment}{Wellcome Open Research}{2020}{}\vspace{-4.0mm}
    \cventry{KAM Gaythorpe, \textcolor{red}{\textbf{A Hamlet}} , L Cibrelus, T Garske, NM Ferguson}{The effect of climate change on yellow fever disease burden in Africa}{Elife}{2020}{}\vspace{-4.0mm}
    \cventry{Kév Jean, \textcolor{red}{\textbf{A Hamlet}} , J Benzler, L Cibrelus, KAM Gaythorpe, A Sall, NM Ferguson, T Garske}{Eliminating yellow fever epidemics in Africa: vaccine demand forecast and impact modelling}{PLoS Neglected Tropical Diseases}{2020}{}\vspace{-4.0mm}
    \cventry{HA Thompson, N Imai, A Dighe, KEC Ainslie, M Baguelin, S Bhatia, S Bhatt, A Boonyasiri, O Boyd, NF Brazeau, L Cattarino, LV Cooper, H Coupland, Z Cucunuba, G Cuomo-Dannenburg, B Djaafara, I Dorigatti, SV Elsland, R FitzJohn, H Fu, KAM Gaythorpe, W Green, T Hallett, \textcolor{red}{\textbf{A Hamlet}} , D Haw, S Hayes, W Hinsley, B Jeffrey, E Knock, DJ Laydon, J Lees, TD Mangal, T Mellan, S Mishra, A Mousa, G Nedjati-Gilani, P Nouvellet, L Okell, KV Parag, M Ragonnet-Cronin, S Riley, HJT Unwin, R Verity, M Vollmer, E Volz, PGT Walker, C Walters, H Wang, Y Wang, OJ Watson, C Whittaker, LK Whittles, P Winskill, X Xi, CA Donnelly, NM Ferguson}{SARS-CoV-2 infection prevalence on repatriation flights from Wuhan City, China}{Journal Of Travel Medicine}{2020}{}\vspace{-4.0mm}
    \cventry{I Dorigatti, \textcolor{red}{\textbf{A Hamlet}} , R Aguas, L Cattarino, A Cori, CA Donnelly, T Garske, N Imai, NM Ferguson}{International risk of yellow fever spread from the ongoing outbreak in Brazil, December 2016 to May 2017}{Eurosurveillance}{2017}{}\vspace{-4.0mm}
    \cventry{D Cantoni, \textcolor{red}{\textbf{A Hamlet}} , M Michaelis, MN Wass, JS Rossman}{Risks posed by Reston, the forgotten ebolavirus}{Msphere}{2016}{}\vspace{-4.0mm}
\end{cventries}



\end{document}
