---
name: Dr Arran Hamlet
date: "`r format(Sys.time(), '%B, %Y')`"
position: Senior Service Fellow
address: "Centers for Disease Control and Prevention"
aboutme: "\\fontsize{10pt}{15pt}\\selectfont Epidemiologist and mathematical modeler skilled at understanding complex real world problems and delivering effective solutions. Highly experienced in statistical modeling, data analytics, and applying problem solving to a wide array of topics. Accomplished in working with and leading diverse teams to successful solutions in outbreak response, disease surveillance, and public health policy."
email: arranh92@gmail.com
github: arranhamlet
linkedin: arranhamlet
output: 
  vitae::awesomecv:
    keep_tex: true
header-includes:
    - \usepackage {hyperref}
    - \hypersetup {colorlinks = true, linkcolor = blue, urlcolor = red}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tidyverse)
library(scholar)
```

# Summary

* 9 years of experience in epidemiology and data analytics, applying mathematical and statistical methods to derive real world solutions in complex situations.
* 9 years of software development and coding, with numerous packages and approaches designed and implemented for use in Academia and Government.
* Highly adept at translating advanced data analytics for non-technical audiences, and applying robust methodological approaches to atypical settings.
* Knowledgeable in advanced statistical and mathematical modeling (mechanistic compartmental modeling, time series forecasting, hierarchical models, etc) and programming (R, shiny).

# Employment
```{r employment}
tribble(
  ~ role, ~ company, ~ loc, ~ dates, ~ details,
  "Senior Service Fellow and Epidemic Intelligence Service Officer", "Centers for Disease Control and Prevention", "Seattle, WA", "Jul 2024-Present and Jul 2022-Jun 2024", "Principle on providing technical assistance to US States and Territories with CDC forecasting and data analytical tools, as well as international engagement with public health agencies in Canada and the European Union.",
 "Senior Service Fellow and Epidemic Intelligence Service Officer", "Centers for Disease Control and Prevention", "Seattle, WA", "Jul 2024-Present and Jul 2022-Jun 2024", "Lead investigator for multiple public health initiatives, heading a multidisciplinary team from local, state and federal agencies to respond to public health threats in Washington state (WA), and abroad, across numerous subject areas. Partnered with CDC subject matter experts and local investigators to estimate and forecast burdens of disease, respond to outbreaks of public health significance, and assess infectious disease surveillance strategies.",
   "Senior Service Fellow and Epidemic Intelligence Service Officer", "Centers for Disease Control and Prevention", "Seattle, WA", "Jul 2024-Present and Jul 2022-Jun 2024", "Produced burden estimates and the potential financial impact of long COVID in WA. Results used by WA lawmakers for raising funding, and findings published in a peer reviewed journal, Preventing Chronic Diseases, where the paper won their “Paper of the Year” award 2024.",
   "Senior Service Fellow and Epidemic Intelligence Service Officer", "Centers for Disease Control and Prevention", "Seattle, WA", "Jul 2024-Present and Jul 2022-Jun 2024", "Led a multidisciplinary team of 10+ experts from Local, State, Federal settings, to investigate the rise in the detection of a rare bacterium in WA. Findings resulted in policy changes to surveillance practices.",
   "Senior Service Fellow and Epidemic Intelligence Service Officer", "Centers for Disease Control and Prevention", "Seattle, WA", "Jul 2024-Present and Jul 2022-Jun 2024", "Investigated an outbreak of gastrointestinal illness on the Pacific Crest Trail. Successful response led to an outbreak resolution, and a change in WA policy on the use of social media in outbreak investigation. The findings were also published in a peer reviewed journal.",
    "Senior Service Fellow and Epidemic Intelligence Service Officer", "Centers for Disease Control and Prevention", "Seattle, WA", "Jul 2024-Present and Jul 2022-Jun 2024", "Assessed the impact of enhanced service delivery and funding, on malaria control and treatment in Uganda during the COVID-19 pandemic. Results indicated that the intervention resulted in maintained, or improved, malaria control despite behavioral changes and logistical issues.",

 
 "Lecturer, technical editor and course designer", "AppliedEpi", "Remote", "Jan 2022-Present", "Leading several streams of work for AppliedEpi, the non-profit behind one of the world's most utilized online free resources for R coding for epidemiologists, The Epidemiologist R Handbook.",
  "Lecturer, technical editor and course designer", "AppliedEpi", "Remote", "Jan 2022-Present", "Taught over a dozen public health agencies globally, including the US CDC, World Health Organization, Canadian Public Health Agency.",
  "Lecturer, technical editor and course designer", "AppliedEpi", "Remote", "Jan 2022-Present", "Created the Advanced Statistics in R course, which has been attended by several hundred epidemiologists across the world.",
  "Lecturer, technical editor and course designer", "AppliedEpi", "Remote", "Jan 2022-Present", "Lead author and editor, coordinating a team of epidemiologists based in 
Sub-Saharan Africa to write chapters on data analysis, regression and outbreak investigation for a new field epidemiology manual aimed at supporting applied epidemiologists in in Lower-middle-income countries.",
   "Lecturer, technical editor and course designer", "AppliedEpi", "Remote", "Jan 2022-Present", "Lead editor on revising the latest version of The Epidemiologist R Handbook, including the updating of text, packages and approaches to ensure the material is state of the art for best practices.",

  "Visiting Researcher", "Imperial College London", "London, United Kingdom", "Jul 2022", "Provide direction and feedback for projects involving the mathematical and statistical modeling of malaria and yellow fever. Continued engagement has resulted in numerous peer reviewed manuscripts.",

 
 "Postdoctoral Research Associate", "Imperial College London", "London, United Kingdom", "Jan 2020-Jun 2022", "Led and participated in numerous applications of statistical and mathematical models to characterize and respond to COVID-19, and reduce the burden of malaria transmission. Utilized and designed software packages and methodological approaches to respond to real world situations in ways that were feasible and offered realistic solutions for partners. Work was conducted with NGO's, local research instiutions and with Ministry's of Health across Sub-Saharan Africa.",
  "Postdoctoral Research Associate", "Imperial College London", "London, United Kingdom", "Jan 2020-Jun 2022", "Led work assessing the potential economic and disease burden impact of an invasive mosquito species in Ethiopia, coordinated with several international partners and the Ethiopian Ministry of Health. Estimates of a significant increase in cases and the millions of USD required to avert them were delivered as a report and peer-reviewed publication that have been highly cited in both policy and academic contexts.",
   "Postdoctoral Research Associate", "Imperial College London", "London, United Kingdom", "Jan 2020-Jun 2022", "Worked with numerous commercial partners and non-profit agencies to forecast the future burden and economic cost of malaria control across Sub-Saharan Africa. These forecasts were used to guide multi-year investment of tens of millions of USD for malaria vector-control program.",
   "Postdoctoral Research Associate", "Imperial College London", "London, United Kingdom", "Jan 2020-Jun 2022", "Lead researcher for Imperial College in a consortium of mathematical modelers providing analytical support and technical assistance to the Nigerian Government’s COVID-19 presidential taskforce. Technical reports and analysis formed part of the basis for policy decisions enacted during 2020.",
    "Postdoctoral Research Associate", "Imperial College London", "London, United Kingdom", "Jan 2020-Jun 2022", "Taught and organized several short courses on the use of mathematical and statistical modeling for infectious disease epidemiology, in the United Kingdom, Brazil and Colombia.",
 
    "Epidemiologist", "World Health Organization", "London, United Kingdom/Geneva, Switzerland", "Jan 2020-Apr 2020", "Seconded to the World Health Organization to provide technical assistance during the early stages of the COVID-19 pandemic. This work provided support to characterize transmission and mortality in real time, to better understand the potential global impact of COVID-19 from January 2020.",
 
 "PhD Candidate", "Imperial College London", "London, United Kingdom", "Jan 2017-Jan 2020", "Fully funded, during which I was awarded several research grants, collectively worth ~£28,000, to organize meetings and shortcourses in Brazil and Colombia, and conduct site visits. Results informed Brazilian Ministry of Health policy, and contributed to several peer-reviewed publications and technical reports with the World Health Organization and Centers for Disease Control and Prevention.",
 
     "Epidemiologist", "World Health Organization", "London, United Kingdom/Geneva, Switzerland", "Jan 2015-Sep 2015", "Supported the response to the 2014-2015 outbreak of Yellow Fever in Angola and the Democratic Republic of the Congo in order to rapidly provide modeling and analytical insight to characterize transmission, and to optimize the geographic placement of vaccination campaigns to stop spread."

) %>% 
  detailed_entries(company, loc, role, dates, details, .protect = F)
```

# Education

```{r education}
tribble(
  ~ degree, ~ uni, ~ loc, ~ dates,
  "PhD in Infectious Disease Epidemiology", "Imperial College London", "London, United Kingdom", "Jan 2017-Jan 2020",
  "MSc in Epidemiology", "Imperial College London", "London, United Kingdom", "Oct 2014-Oct 2015",
  "BSc in Biology with Psychology", "Queen Mary University of London", "London, United Kingdom", "Sep 2011-May 2014"
) %>% 
  detailed_entries(uni, loc, degree, dates)
```

```{r publications_load, echo = FALSE, message = FALSE, warning = FALSE, results = FALSE}
pubs <- scholar::get_publications("xk9BhHUAAAAJ")%>%
  dplyr::mutate(author = author %>%
                  as.character,
                journal = journal %>%
                  replace(journal %in% "bioRxiv", "BioRxiv") %>%
                  replace(journal %in% "medRxiv", "MedRxiv"),
                first_author = case_when(stringr::str_starts(author, "A Hamlet|ATP Hamlet") ~ TRUE,
                                         TRUE ~ FALSE),
                preprint = case_when(journal %in% c("bioRxiv", "BioRxiv", "MedRxiv", "medRxiv", "") ~ TRUE,
                                     TRUE ~ FALSE),
                report = case_when(stringr::str_starts(title, "Report") ~ TRUE,
                                   TRUE ~ FALSE)) %>%
  dplyr::arrange(desc(year), desc(cites))

# print(pubs)
predict_h_index <- function(id, journals = NULL) {
    id <- tidy_id(id)

    # Getting the h-index and checking for NA
    h <- get_profile(id)$h_index
    if (is.na(h)) return(NA)

    n <- get_num_articles(id) # number of articles written
    y <- as.numeric(format(Sys.Date(), "%Y")) - get_oldest_article(id)
    j <- get_num_distinct_journals(id)

    # Handle optional journals parameter
    if (is.null(journals)) {
        q <- get_num_top_journals(id)
    } else {
        q <- get_num_top_journals(id, journals)
    }

    # Regression coefficients
    coefs <- c(
        1, 0.760, 0.373, 0.967, -0.069, 0.018, 0.033,
        2, 1.413, 0.781, 0.936, -0.132, 0.018, 0.064,
        3, 2.227, 1.105, 0.903, -0.193, 0.027, 0.096,
        4, 3.196, 1.386, 0.871, -0.274, 0.039, 0.145,
        5, 3.997, 1.578, 0.858, -0.345, 0.063, 0.198,
        6, 4.752, 1.671, 0.817, -0.377, 0.117, 0.282,
        7, 5.741, 1.761, 0.761, -0.420, 0.170, 0.394,
        8, 6.531, 1.796, 0.669, -0.420, 0.252, 0.508,
        9, 7.482, 1.653, 0.561, -0.415, 0.383, 0.629,
        10, 8.734, 1.326, 0.478, -0.411, 0.522, 0.823
    )
    coefs.m <- matrix(coefs, nrow=10, byrow=TRUE)
    coefs <- coefs.m[,-1]
    vals <- c(1, sqrt(n), h, y, j, q)

    # Calculate the h-index predictions
    h.pred <- coefs %*% vals
    h.vals <- c(h, h.pred)

    # Check for sensible values
    standard.warning <- "You're probably not a neuroscientist. Please read the documentation for information on the limitations of this function."
  
    if (any(diff(h.vals) < 0)) {
        warning(paste0("Decreasing h-values predicted. ", standard.warning))
    }

    if (any(h.vals < 0)) {
        warning(paste0("Negative h-values predicted. ", standard.warning))
    }
  
    return(data.frame(years_ahead = 0:10, h_index = h.vals))
}

predict_h_index("xk9BhHUAAAAJ")


pubs <- pubs %>%
  rowwise() %>%
  mutate(
    author = case_when(
      str_ends(author, "\\.\\.\\.") ~ get_complete_authors(id = "xk9BhHUAAAAJ", pubid = pubid),
      TRUE ~ author
    )
  )


# pubs <- pubs[-which(pubs$cites == 0 and pubs$year < 2021), ]
if(any(duplicated(pubs$title))) pubs <- pubs[-which(duplicated(pubs$title)), ]
pubs <- pubs[!is.na(pubs$year), ]
pubs$author <- gsub("A Hamlet|ATP Hamlet", "\\\\textcolor{red}{\\\\textbf{A Hamlet}} ", pubs$author)

#Fix journal names
pubs <- pubs %>%
  mutate(
    journal = str_to_title(journal),
    journal = gsub("Plos", "PLoS", journal),
    journal = gsub("Bmc", "BMC", journal),
    journal = case_when(
    journal == "Bmj" ~ "BMJ",
    TRUE ~ journal
  )) %>%
  filter(!grepl("vol 6, pg e100|Imperial College", title))

name_in_first_couple <- pubs[which(pubs$first_author == F & grepl("Hamlet", pubs$author)), ]
name_in_first_couple_papers <- name_in_first_couple[which(name_in_first_couple$report == F & name_in_first_couple$preprint == F), ]

first_author_number <- pubs %>% dplyr::filter(first_author == T & preprint == F) %>% nrow()
other_author_number <- name_in_first_couple_papers %>% nrow()
  
```


# Presentations and publications
Presented results of outbreak investigations, scientific analysis and data analytical approaches at over a dozen international conferences, meetings and workshops. 

Author of **`r first_author_number`** first author publications, and co-author on additional **`r other_author_number`**. Cited **`r get_citation_history("xk9BhHUAAAAJ") %>% pull(cites) %>% sum() %>% format(scientific = FALSE, big.mark = ",")`** times, with a h-index of **`r subset(predict_h_index("xk9BhHUAAAAJ"), years_ahead == 0) %>% pull(h_index)`**.

For a full list of publications, please see my [<span style="color: red">**Google Scholar profile**</span>](https://scholar.google.co.uk/citations?user=xk9BhHUAAAAJ&hl=en).



